---
title: "p8105_hw5_bes2161"
author: "Brittany Shea"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidyr)
library(lubridate)
library(rvest)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

# Import, map, and unnest data:

```{r}
full_df = 
  tibble(
    files = list.files("data/prob_1/"),
    path = str_c("data/prob_1/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

# Tidy the data:

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

# Plot data on subjects over time faceted by group:

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

We see high within-subject correlation, and subjects in the control group do not change much over time whereas the outcome for the experiment group increases linearly.

## Problem 2

# Load and describe data:

```{r}
wp = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate_if(is.character, str_to_lower) %>% 
  unite("city_state", city:state, sep = ", ") %>% 
  mutate(reported_date = lubridate::ymd(reported_date))
```

This data frame includes data from the Washington Post on homicides in 50 large U.S. cities. There are 52,179 rows and 12 columns. It includes variables: id; report date; victim first and last names; victim race, age, and sex; city and state; longitude and latitude; and disposition.

# Tidy the data:

```{r}
homicides = wp %>% 
  mutate(unsolved = disposition == "closed without arrest" | disposition == "open/no arrest") %>%
  group_by(city_state) %>% 
  summarise(
    total = n(),
    unsolved = sum(unsolved)
  )

```

# Baltimore:

```{r}
baltimore = homicides %>% 
  filter(city_state == "baltimore, md")

prop.test(
  x = pull(baltimore, unsolved),
  n = pull(baltimore, total)) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))

```

# Function:

```{r}
prop_func = function(alpha, beta) {
  prop.test(x = alpha, n = beta) %>% 
  broom::tidy() %>% 
  select(estimate, starts_with("conf"))
}

homicides = homicides %>% 
  mutate(output = purrr::map2(unsolved, total, prop_func)) %>% 
  unnest()

```

# Plot:

```{r}
homicides %>%
  mutate(
    estimate = str_c("n = ", estimate),
    estimate = fct_inorder(estimate)) %>% 
  ggplot(aes(x = city_state)) + 
  geom_bar() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 1) +
  labs(title = "Estimates and CIs by City") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
    
```

## Problem 3

# Function:

```{r}
sim_t_test = function(m) {
  
  sample = rnorm(30, mean = m, sd = 5)
  
  t.test(sample) %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
}

```

# Iterate: 

```{r}
sim_results_df =
  expand_grid(
    true_mean = 0:6,
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(true_mean, sim_t_test)
  ) %>% 
  unnest(estimate_df)

```

# Plot:

```{r}
sim_results_df %>% 
  mutate(
     signif = case_when(
       p.value < .05 ~ "signif",
       p.value > .05 ~ "not_signif",
       TRUE ~ ""
       )) %>%
  group_by(true_mean, signif) %>% 
  ggplot(aes(x = true_mean, y = estimate, colour = signif)) + 
  geom_violin()

```

This plot shows the fraction of times the p.value is less than .05. We can see that power increases as the true mean increases.

# Plot:

```{r}
sim_results_df %>% 
  group_by(true_mean, estimate) %>% 
  ggplot(aes(x = true_mean, y = estimate)) + 
  geom_point()

sim_results_df %>% 
  mutate(
     signif = case_when(
       p.value < .05 ~ "signif",
       p.value > .05 ~ "not_signif",
       TRUE ~ ""
       )) %>%
  filter(signif != "not_signif") %>% 
  group_by(true_mean, estimate) %>% 
  ggplot(aes(x = true_mean, y = estimate)) + 
  geom_point()

```

No, the two means are not the same. When we have low power, the means are really different. This emphasizes the need to be skeptical when reporting results.
